---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# RIVD

<!-- badges: start -->
<!-- badges: end -->

The goal of RIVD is to deliver simple tools and adapted outputs for in vitro diagnostic (IVD) assay performances assessment. The results can be used in early assay development phase or hopefully with compliance with regulatory frameworks. The package is built according to the recommandation formulated in the CLSI guidelines.

## Installation

<!-- You can install the released version of RIVD from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("RIVD") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Felixmil/RIVD")
```
## Example

Performance report for assay's precision.

```{r example}
library(RIVD)
library(knitr)
library(magrittr)
data(Glucose,package="VCA")

perfPrecision(Glucose, 'result','run', 'day') %>% kable()
```

Plot of data points
```{r}
library(RIVD)
data(Glucose,package="VCA")
plotPrecision(Glucose, 'result','run', 'day')
```

